Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2016-09-21 Draft.tex
Add brief supplementary materials section
Modify caption for readability.

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Oral Prelim/Posteriors_Families_draft"}
\caption{\label{fig:sim2typical} 
Representative example of the posterior distributions for $\pdet$ simulated from nonpeaked gamma (shape$<$1), exponential (shape$=$1), and peaked gamma (shape$>$1) mixture TTDDs, fit with exponential (light solid line) and gamma (dark solid line), and compared to the true detection probability (dashed vertical line, $\pdet=0.8$). 
% Representative example of posterior distributions for $\pdet$.  Data derive from mixture TTDDs of nonpeaked gamma, exponential, and peaked gamma families, and are fit with inference models from exponential and gamma families.  The vertical dashed line presents the true value of $\pdet = 0.80$.
}
\end{figure}

@@

>>>>

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Oral Prelim/Posteriors_Families_draft"}
\caption{\label{fig:sim2typical} 
Representative example of the posterior distributions for $\pdet$ from exponential (light solid line) and gamma (dark solid line) mixture models fit to data simulated from nonpeaked gamma (shape$<$1), exponential (shape$=$1), and peaked gamma (shape$>$1) mixture TTDDs, with true detection probabilities shown for comparison (dashed vertical line, $\pdet=0.8$). 
}
\end{figure}

@@

\section{Supplementary Materials}

The supplementary materials include supplementary figures as well as code to fit these models.
